### 2023-12-02 MSFT.Rmd
First Prototype for VAR Analysis

---
title: "The Impact of ChatGPT news on MSFT"
author: "Ansam Zedan, Daniel Wullschleger"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Insert introduction here

First we get the MSFT price data via yahoo API and we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.

```{r echo=FALSE}
if (!require("vars")) install.packages("vars", dependencies=TRUE)
if (!require("tseries")) install.packages("tseries", dependencies=TRUE)
if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)

library(vars)
library(tseries)
library(quantmod)

MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-11-18", periodicity = "daily", auto.assign=FALSE)[,6]

adf.test(MSFT) 
```

We see that based on the p-value of the ADF Test, that the price data itself is non-stationary.
So we a apply a log-transform with subsequent differencing to calculate continuous returns on MSFT.
These should behave stationary.

```{r pressure, echo=FALSE}
MSFT_returns <- na.omit(diff(log(MSFT)))
adf.test(MSFT_returns)
```
Now, that we deal with stationary data we can begin with our analysis.

First we include the ChatGPT News Time Series to then create a Vector Autoregression model as we want to find out, whether ChatGPT News are a causal driver for MSFT price returns.

We then do a coefficient test, to get more information on the statistical significance of the coefficients of our VAR Model.

```{r pressure, echo=FALSE}
coeftest(VAR_est)
MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)

```

As not all coeffcients are signifcant, we may do a causality test. This way, we can find out, if ChatGPT News are in fact a causal driver for MSFT prices

```{r pressure, echo=FALSE}

causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
causality(VAR_est, cause="Inflation_CH")["Granger"]

```

Lastly, it would be interesting to find out how ChatGPT News actually influence the MSFT price returns. So that we may estimate long  such news do have effect on the price.

For this we simulate shocks to the system

```{r pressure, echo=FALSE}

plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))

```

### 2023-12-02 MSFT.r

@@ -1,6 +1,0 @@
-install.packages("quantmod")
-
-library(quantmod)
-
-MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-11-18", periodicity = "daily", auto.assign=FALSE)[,6]
-MSFT

### 2023-12-02 MSFT.Rmd
included some plots

@@
 
-First we get the MSFT price data via yahoo API and we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.
+First we get the recent MSFT price data from the beginning of 2022 up to today via yahoo API and plot it so that we can inspect if the time series already behaves stationary
 
-```{r echo=FALSE}
+```{r echo=FALSE, include=TRUE}
 if (!require("vars")) install.packages("vars", dependencies=TRUE)
@@
 
-MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-11-18", periodicity = "daily", auto.assign=FALSE)[,6]
+MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
 
+ChatGPT <- read.csv("ChatGPT.csv")
+
+plot(MSFT)
+```
+We see a clear trend, which is an indicator for non-stationarity, so we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.
+
+```{r echo=FALSE, include=TRUE}
 adf.test(MSFT) 
@@
 
-```{r pressure, echo=FALSE}
+```{r echo=FALSE, include=TRUE}
 MSFT_returns <- na.omit(diff(log(MSFT)))
 adf.test(MSFT_returns)
+
+plot(MSFT_returns)
 ```
@@
 
-```{r pressure, echo=FALSE}
+```{r echo=FALSE, include=TRUE}
 coeftest(VAR_est)
@@
 
-```{r pressure, echo=FALSE}
-
+```{r echo=FALSE, include=TRUE}
 causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
@@
 
-```{r pressure, echo=FALSE}
-
+```{r echo=FALSE, include=TRUE}
 plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))

### 2023-12-02 MSFT.Rmd
included GARCH and dummy ChatGPT code

@@
 if (!require("quantmod")) install.packages("quantmod", dependencies=TRUE)
+if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics", dependencies=TRUE)
+if (!require("forecast")) install.packages("forecast", dependencies=TRUE)
+if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)
 
+library(PerformanceAnalytics)
+library(forecast)
+library(rugarch)
 library(vars)
@@
 
-ChatGPT <- read.csv("ChatGPT.csv")
+#ChatGPT <- read.csv("ChatGPT.csv")
 
@@
 MSFT_returns <- na.omit(diff(log(MSFT)))
+colnames(MSFT_returns)<-"MSFT_Returns"
 adf.test(MSFT_returns)
@@
 coeftest(VAR_est)
-MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
+#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
 
@@
 ```{r echo=FALSE, include=TRUE}
-causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
-causality(VAR_est, cause="Inflation_CH")["Granger"]
+#causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
+#causality(VAR_est, cause="Inflation_CH")["Granger"]
 
@@
 ```{r echo=FALSE, include=TRUE}
-plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))
+#plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))
 
 ```
+
+GARCH Model:
+
+For our GARCH model we calculate a 30-day rolling volatility
+
+```{r echo=FALSE, include=TRUE}
+chart.RollingPerformance(R = MSFT_returns, width = 30,
+                         FUN = "sd.annualized", scale = 252, main = "30-day rolling volatility")
+
+```
+To setup a GARCH Model for our MSFT analysis we have to specify the orders of an ARMA model as well as a GARCH Model.
+
+From class we learned, that in Finance is it common to stick to a GARCH(1,1) model, so we just need to estimate the ARMA model orders. For this, we let auto.arima find the best fitting orders
+
+```{r echo=FALSE, include=TRUE}
+auto.arima(MSFT_returns)
+```
+
+We see that auto.arima has found that the auto-regressive (AR) part of the ARMA model has an order of 2 present as the coefficients ar1 and ar2 were estimated.
+The Absence of ma coefficients suggests that the Moving Average (MA) part has an order of 0.
+
+Now we can specify our GARCH model and fit it to our data.
+
+```{r echo=TRUE, include=TRUE}
+MSFT_garch_spec <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = TRUE),
+                        variance.model = list(garchOrder = c(1,1), model = "sGARCH"))
+
+MSFT_garch_fit <- ugarchfit(data = MSFT_returns, spec = MSFT_garch_spec)
+```
+
+Now we can use the sigma method to extract the estimated GARCH volatilities, so that we can plot them on a chart
+
+```{r echo=FALSE, include=TRUE}
+MSFT_volatility <- sigma(MSFT_garch_fit)
+
+par(mfrow=c(2,1)) 
+plot(MSFT_volatility, main="MSFT GARCH volatility")
+plot(abs(MSFT_returns), main="Realized volatility")
+```
+
+AS a last step, we may forecast the returns and volatility values.
+Here, ARMA will estimate the returns, while GARCH estimates the volatilities
+
+```{r echo=FALSE, include=TRUE}
+par(mfrow=c(1,1))
+MSFT_volatility_forecast <- ugarchforecast(fitORspec = MSFT_garch_fit, n.ahead = 5)
+plot(MSFT_volatility_forecast, which=1)
+plot(MSFT_volatility_forecast, which=3)
+```
+
+```{r echo=FALSE, include=TRUE}
+auto.arima(MSFT_returns)
+```
+
+```{r echo=FALSE, include=TRUE}
+auto.arima(MSFT_returns)
+```
+
+```{r echo=FALSE, include=TRUE}
+auto.arima(MSFT_returns)
+```

### 2023-12-02 MSFT.Rmd
Included gitIgnore and tinytex

@@
 
-# Insert introduction here
-
-First we get the recent MSFT price data from the beginning of 2022 up to today via yahoo API and plot it so that we can inspect if the time series already behaves stationary
-
-```{r echo=FALSE, include=TRUE}
+```{r include=FALSE}
 if (!require("vars")) install.packages("vars", dependencies=TRUE)
@@
 library(quantmod)
+library(tinytex)
+```
+# Insert introduction here
 
+First we get the recent MSFT price data from the beginning of 2022 up to today via yahoo API and plot it so that we can inspect if the time series already behaves stationary
+
+```{r echo=FALSE, include=TRUE}
 MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
@@
 ```{r echo=FALSE, include=TRUE}
-coeftest(VAR_est)
 #MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
-
+#coeftest(MSFT_VAR)
 ```

### 2023-12-02 MSFT.Rmd
ARMA prediction

@@
 ---
-title: "The Impact of ChatGPT news on MSFT"
+title: "The Impact of News Sentiment on MSFT"
 author: "Ansam Zedan, Daniel Wullschleger"
@@
 if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)
+if (!require("tinytex")) install.packages("tinytex", dependencies=TRUE)
+if (!require("zoo")) install.packages("zoo", dependencies=TRUE)
+if (!require("ggplot2")) install.packages("ggplot2", dependencies=TRUE)
 
@@
 library(tinytex)
+library(zoo)
+library(ggpl)
 ```
@@
 #ChatGPT <- read.csv("ChatGPT.csv")
-
 plot(MSFT)
@@
 We see that based on the p-value of the ADF Test, that the price data itself is non-stationary.
-So we a apply a log-transform with subsequent differencing to calculate continuous returns on MSFT.
-These should behave stationary.
+So we a apply a log-transform with subsequent differencing to calculate continuous returns on MSFT. These should behave stationary.
+
+In the same step, we divide the dataset into a Train/Test Split, whereas November 2023 will serve as a test set for later predicitions
 
@@
 colnames(MSFT_returns)<-"MSFT_Returns"
-adf.test(MSFT_returns)
+
+MSFT_returns_test <- window(MSFT_returns, start="2023-10-01")
+MSFT_returns_train <- window(MSFT_returns, end="2023-09-30")
 
 plot(MSFT_returns)
+adf.test(MSFT_returns)
 ```
@@
 
-First we include the ChatGPT News Time Series to then create a Vector Autoregression model as we want to find out, whether ChatGPT News are a causal driver for MSFT price returns.
+First we include the News Time Series to then create a Vector Autoregression model as we want to find out, whether News are a causal driver for MSFT price returns.
 
@@
 ```{r echo=FALSE, include=TRUE}
-#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
+#MSFT_VAR <- VAR(cbind(MSFT_returns_train, ChatGPT), ic="AIC", lag.max = 24)
 #coeftest(MSFT_VAR)
@@
 
-As not all coeffcients are signifcant, we may do a causality test. This way, we can find out, if ChatGPT News are in fact a causal driver for MSFT prices
+As not all coeffcients are signifcant, we may do a causality test. This way, we can find out, if  News are in fact a causal driver for MSFT prices
 
@@
 
-Lastly, it would be interesting to find out how ChatGPT News actually influence the MSFT price returns. So that we may estimate long  such news do have effect on the price.
+Lastly, it would be interesting to find out how  News actually influence the MSFT price returns. So that we may estimate long  such news do have effect on the price.
 
@@
 #plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))
+
+```
+
+As a benchmark for our VAR Model that features News sentiment as a predictor, we use an ARMA model that is purely based on the price returns of MSFT.
+This way, we can forecast values of November 2023 and compare the predictions to the actual MSFT price returns to measure its accuracy.
+
+MSFT_prediction <- predict
+
+```{r echo=FALSE, include=TRUE}
+MSFT_benchmark_ARMA <- auto.arima(MSFT_returns_train)
+MSFT_benchmark_pred <- forecast(MSFT_benchmark_ARMA, level=95, h=43)
+
+plot(MSFT_benchmark_pred)
 
@@
 
-From class we learned, that in Finance is it common to stick to a GARCH(1,1) model, so we just need to estimate the ARMA model orders. For this, we let auto.arima find the best fitting orders
+From class we learned, that in Finance it is common to stick to a GARCH(1,1) model, so we just need to estimate the ARMA model orders. For this, we let auto.arima find the best fitting orders
 
@@
 
-AS a last step, we may forecast the returns and volatility values.
+As a last step, we may forecast the returns and volatility values.
 Here, ARMA will estimate the returns, while GARCH estimates the volatilities

### 2023-12-03 MSFT_code_trials.R
sentiment analysis

@@ -1,0 +1,15 @@
+library(PerformanceAnalytics)
+library(forecast)
+library(rugarch)
+library(vars)
+library(tseries)
+library(quantmod)
+library(tinytex)
+library(zoo)
+library(ggpl)
+
+MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
+
+head(MSFT)
+
+write.zoo(MSFT, "MSFT.csv", sep = ",", row.names = TRUE)

### 2023-12-09 MSFT.Rmd
Included Introduction, Removed GARCH parts, Included VAR model and Prediction + Comparison with Testset

--- 2023-12-02 MSFT.Rmd
@@
 if (!require("rugarch")) install.packages("rugarch", dependencies=TRUE)
+if (!require("tinytex")) install.packages("tinytex", dependencies=TRUE)
+if (!require("zoo")) install.packages("zoo", dependencies=TRUE)
+if (!require("ggpl")) install.packages("ggpl", dependencies=TRUE)
 
@@
 library(quantmod)
+library(tinytex)
+library(zoo)
+library(ggpl)
+```
+# Insert introduction here
+In recent years Microsoft has pushed and achieved great progress in a diverse portfolio of technologies (Microsoft, 2022) including also partnerships with AI research centers such as OpenAI.
+Alongside this development, its stock price has since reached new all-time highs and persists to be a major player in tech investments.
 
-MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
+Inspired by this evolution, this paper provides an analysis and forecast of the stock price of Microsoft based on news sentiment data from subreddits such as r/worldnews, r/investing and r/stocks using a vector autoregressive (VAR) model.
 
-#ChatGPT <- read.csv("ChatGPT.csv")
+Vector Autoregressive (VAR) processes are popular in economics for their flexibility and simplicity as models for multivariate time series data, forming a vector between variables that affect each other (Suharsono et al.
+2017; Aptech 2021).
+The relationship between the stock prices and the news events will be analysed using a Granger causality testing, similarly as Bhowmik et al.
+(2022) proceeded when comparing multiple markets.
 
-plot(MSFT)
-```
-We see a clear trend, which is an indicator for non-stationarity, so we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is already stationary.
+Hereby MSFT price data was downloaded through the Yahoo API in R and Reddit posts were scraped using Jupyter Notebooks.
+The python libraries nltk, textblob and wordlcoud were of support in the creation of the sentiment scores.
+
+Analysis:
+First, we import the data and convert it to a time series so that we may plot it
 
 ```{r echo=FALSE, include=TRUE}
-adf.test(MSFT) 
+MSFT <- read.csv("data/final_data.csv")
+MSFT$Index <- as.Date(MSFT$Index)
+MSFT$MSFT.Adjusted <- as.numeric(as.character(MSFT$MSFT.Adjusted))
+MSFT$average_polarity <- as.numeric(as.character(MSFT$average_polarity))
+MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
+
+plot(MSFT_ts)
+```
+We see a clear trend, which is an indicator for non-stationarity, so we do an Augmented Dickey-Fuller (ADF) Test to see whether the data is in fact non-stationary.
+
+```{r echo=FALSE, include=TRUE}
+adf.test(MSFT_ts) 
 ```
 
-We see that based on the p-value of the ADF Test, that the price data itself is non-stationary.
+We see that based on the p-value of 0.7051 the ADF Test suggests that the price data is non-stationary.
 So we a apply a log-transform with subsequent differencing to calculate continuous returns on MSFT.
@@
 
+In the same step, we divide the dataset into a Train/Test Split, whereas November 2023 will serve as a test set for later predicitions
+
 ```{r echo=FALSE, include=TRUE}
-MSFT_returns <- na.omit(diff(log(MSFT)))
-colnames(MSFT_returns)<-"MSFT_Returns"
-adf.test(MSFT_returns)
+MSFT_returns <- na.omit(diff(log(MSFT_ts)))
+MSFT_returns
+
+MSFT_returns_train <- window(MSFT_returns, sart ="2022-01-04", end="2023-09-30")
+MSFT_returns_test <- window(MSFT_returns, start="2023-10-01")
 
 plot(MSFT_returns)
+adf.test(MSFT_returns)
 ```
@@
 
-First we include the ChatGPT News Time Series to then create a Vector Autoregression model as we want to find out, whether ChatGPT News are a causal driver for MSFT price returns.
+First we create a time series of news sentiment data.
+Combined with the price returns, we can create a Vector Autoregression model.
+This will be our basis to check whether News are a causal driver for MSFT price returns.
 
@@
 ```{r echo=FALSE, include=TRUE}
-coeftest(VAR_est)
-#MSFT_VAR <- VAR(cbind(MSFT_returns, ChatGPT), ic="AIC", lag.max = 24)
+news_ts <- zoo(MSFT$average_polarity, order.by = MSFT$Index)
+news_train <- window(news_ts, start ="2022-01-04", end="2023-09-30")
+news_test <- window(news_ts, start="2023-10-01")
+MSFT_VAR_Data <- cbind(MSFT_returns_train, news_train)
+colnames(MSFT_VAR_Data) <- c("MSFT_Returns", "News_Sentiment")
+
+MSFT_VAR <- VAR(MSFT_VAR_Data, ic="AIC", lag.max = 24)
+coeftest(MSFT_VAR)
+```
+
+We see that almost none of the coefficients have a statistical significance.
+As a next step, we do a Granger causality test to confirm that news data is in fact non a causal driver for the MSFT stock price
+
+```{r echo=FALSE, include=TRUE}
+causality(MSFT_VAR, cause="News_Sentiment")["Granger"] 
+```
+The p-value of 0.34 suggests that the gathered News sentiments are not a causal driver for the MSFT stock price. This leads us to reject our hypothesis.
+
+However, from a practical point of view, our VAR model may still be of some use when applied for forecasting purposes.
+To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy in predicting the price movements of MSFT we do some forecasting for our testing period.
+
+At the same time, we setup an ARMA model that is purely based on MSFTs previous price movements. It will serve as our benchmark.
+
+```{r echo=FALSE, include=TRUE}
+forecast <- predict(MSFT_VAR, n.ahead = length(news_test))
+plot(forecast)
+MSFT_VAR_pred <- forecast$fcst$MSFT_Returns
+
+rmse_VAR <- sqrt(mean((MSFT_returns_test - MSFT_VAR_pred)^2))
+rmse_VAR
+
+MSFT_ARMA <- auto.arima(MSFT_returns_train)
+MSFT_ARMA_pred <- forecast(MSFT_benchmark_ARMA, level=95, h = length(news_test))
+plot(MSFT_ARMA_pred)
+
+rmse_ARMA <- sqrt(mean((MSFT_returns_test - MSFT_ARMA_pred$mean)^2))
+rmse_ARMA
+
+```
+We see that auto.arima has found that the auto-regressive (AR) part of our benchmark ARMA model has an order of 2, since the coefficients ar1 and ar2 were estimated.
+The Absence of ma coefficients suggests that the Moving Average (MA) part has an order of 0.
+Therefore, we essentially deal with an AR(2) model as our benchmark.
+During forecasting, we also see that it uses a mean of 0 with a confidence band for all future values.
+This makes sense, as we deal with stationary data that commonly has a mean of 0.
+
+While the VAR model reaches an RSME of 0.036 when compared to the truth values of our test set, the AR(2) benchmark reaches an RSME of 0.014.
+This means, our more sophisticated VAR model actually performs worse than the more simple AR(2) that is purely based on past values.
+
+```{r echo=FALSE, include=TRUE}
 
@@
 
-As not all coeffcients are signifcant, we may do a causality test. This way, we can find out, if ChatGPT News are in fact a causal driver for MSFT prices
+Bibliography:
 
-```{r echo=FALSE, include=TRUE}
-#causality(MSFT_VAR, cause="ChatGPT")["Granger"] 
-#causality(VAR_est, cause="Inflation_CH")["Granger"]
+Agus Shuarsono, Auliya Aziza and Wara Pramesti (2017); Comparison of vector autoregressive (VAR) and vector error correction models (VECM) for index of ASEAN stock price. DOI 10.1063/1.5016666
 
-```
+Aptech, Introduction to the Fundamentals of Vector Autoregressive Models (2021). https://www.aptech.com/blog/introduction-to-the-fundamentals-of-vector-autoregressive-models/
 
-Lastly, it would be interesting to find out how ChatGPT News actually influence the MSFT price returns. So that we may estimate long  such news do have effect on the price.
+Microsoft, 2022 a look back at a year of accelerating progress in AI.
+https://www.microsoft.com/en-us/research/blog/2022-a-look-back-at-a-year-of-accelerating-progress-in-ai/
 
-For this we simulate shocks to the system
-
-```{r echo=FALSE, include=TRUE}
-#plot(irf(VAR_est, impulse="ChatGPT", response="MSFT_returns"))
-
-```
-
-GARCH Model:
-
-For our GARCH model we calculate a 30-day rolling volatility
-
-```{r echo=FALSE, include=TRUE}
-chart.RollingPerformance(R = MSFT_returns, width = 30,
-                         FUN = "sd.annualized", scale = 252, main = "30-day rolling volatility")
-
-```
-To setup a GARCH Model for our MSFT analysis we have to specify the orders of an ARMA model as well as a GARCH Model.
-
-From class we learned, that in Finance is it common to stick to a GARCH(1,1) model, so we just need to estimate the ARMA model orders. For this, we let auto.arima find the best fitting orders
-
-```{r echo=FALSE, include=TRUE}
-auto.arima(MSFT_returns)
-```
-
-We see that auto.arima has found that the auto-regressive (AR) part of the ARMA model has an order of 2 present as the coefficients ar1 and ar2 were estimated.
-The Absence of ma coefficients suggests that the Moving Average (MA) part has an order of 0.
-
-Now we can specify our GARCH model and fit it to our data.
-
-```{r echo=TRUE, include=TRUE}
-MSFT_garch_spec <- ugarchspec(mean.model = list(armaOrder = c(2,0), include.mean = TRUE),
-                        variance.model = list(garchOrder = c(1,1), model = "sGARCH"))
-
-MSFT_garch_fit <- ugarchfit(data = MSFT_returns, spec = MSFT_garch_spec)
-```
-
-Now we can use the sigma method to extract the estimated GARCH volatilities, so that we can plot them on a chart
-
-```{r echo=FALSE, include=TRUE}
-MSFT_volatility <- sigma(MSFT_garch_fit)
-
-par(mfrow=c(2,1)) 
-plot(MSFT_volatility, main="MSFT GARCH volatility")
-plot(abs(MSFT_returns), main="Realized volatility")
-```
-
-AS a last step, we may forecast the returns and volatility values.
-Here, ARMA will estimate the returns, while GARCH estimates the volatilities
-
-```{r echo=FALSE, include=TRUE}
-par(mfrow=c(1,1))
-MSFT_volatility_forecast <- ugarchforecast(fitORspec = MSFT_garch_fit, n.ahead = 5)
-plot(MSFT_volatility_forecast, which=1)
-plot(MSFT_volatility_forecast, which=3)
-```
-
-```{r echo=FALSE, include=TRUE}
-auto.arima(MSFT_returns)
-```
-
-```{r echo=FALSE, include=TRUE}
-auto.arima(MSFT_returns)
-```
-
-```{r echo=FALSE, include=TRUE}
-auto.arima(MSFT_returns)
-```
+Roni Bhowmik, Gouranga Chandra Debnath, Nitai Chandra Debnath, Shouyang Wang (2022); Emerging stock market reactions to shocks during various crisis periods 2022). DOI 10.1371/journal.pone.0272450

### 2023-12-09 MSFT_code_trials.R

@@ -1,15 +1,6 @@
-library(PerformanceAnalytics)
-library(forecast)
-library(rugarch)
-library(vars)
-library(tseries)
+# This Script was used to get the Price data on MSFT, so that we can enrich
+# the data with News data and their sentiment scores via python script
+
 library(quantmod)
-library(tinytex)
-library(zoo)
-library(ggpl)
-
 MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
-
-head(MSFT)
-
 write.zoo(MSFT, "MSFT.csv", sep = ",", row.names = TRUE)

### 2023-12-09 MSFT.Rmd
Included news sentiment of testing period while predicting the future values

@@
 However, from a practical point of view, our VAR model may still be of some use when applied for forecasting purposes.
-To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy in predicting the price movements of MSFT we do some forecasting for our testing period.
+To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the news sentiment data of the testing period.
 
@@
 ```{r echo=FALSE, include=TRUE}
-forecast <- predict(MSFT_VAR, n.ahead = length(news_test))
+forecast_data <- data.frame(
+  MSFT_Returns = rep(NA, length(news_test)),
+  News_Sentiment = news_test
+)
+
+forecast <- predict(MSFT_VAR, newdata = forecast_data, n.ahead=43)
 plot(forecast)

### 2023-12-09 MSFT.Rmd
fixed some bugs

@@
 if (!require("zoo")) install.packages("zoo", dependencies=TRUE)
-if (!require("ggpl")) install.packages("ggpl", dependencies=TRUE)
+if (!require("ggplot2")) install.packages("ggplot2", dependencies=TRUE)
 
@@
 library(zoo)
-library(ggpl)
+library(ggplot2)
 ```
@@
 MSFT_ARMA <- auto.arima(MSFT_returns_train)
-MSFT_ARMA_pred <- forecast(MSFT_benchmark_ARMA, level=95, h = length(news_test))
+MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(news_test))
 plot(MSFT_ARMA_pred)

### 2023-12-09 MSFT.Rmd
fixed title

@@
 ```
-# Insert introduction here
+#Introduction
 In recent years Microsoft has pushed and achieved great progress in a diverse portfolio of technologies (Microsoft, 2022) including also partnerships with AI research centers such as OpenAI.
@@
 
-Analysis:
+#Analysis
 First, we import the data and convert it to a time series so that we may plot it

### 2023-12-09 MSFT.Rmd
fixed titles

@@
 ```
-#Introduction
+# Introduction 
 In recent years Microsoft has pushed and achieved great progress in a diverse portfolio of technologies (Microsoft, 2022) including also partnerships with AI research centers such as OpenAI.
@@
 
-#Analysis
+# Analysis:
 First, we import the data and convert it to a time series so that we may plot it

### 2023-12-09 MSFT.Rmd
Reformatted the the Rmd

@@
 # Analysis:
-First, we import the data and convert it to a time series so that we may plot it
+First, we import the data and convert it to a time series so that we may plot it.
 
@@
 ```
-
+## Achieving Stationarity
 We see that based on the p-value of 0.7051 the ADF Test suggests that the price data is non-stationary.
@@
 
-In the same step, we divide the dataset into a Train/Test Split, whereas November 2023 will serve as a test set for later predicitions
-
 ```{r echo=FALSE, include=TRUE}
 MSFT_returns <- na.omit(diff(log(MSFT_ts)))
-MSFT_returns
-
-MSFT_returns_train <- window(MSFT_returns, sart ="2022-01-04", end="2023-09-30")
-MSFT_returns_test <- window(MSFT_returns, start="2023-10-01")
 
@@
 ```
+## Creating a VAR Model using News sentiment
 Now, that we deal with stationary data we can begin with our analysis.
+
+We divide the dataset into a Train/Test Split, whereas November and December 2023 will serve as a test set for later predicitions.
 
@@
 news_ts <- zoo(MSFT$average_polarity, order.by = MSFT$Index)
+
+MSFT_returns_train <- window(MSFT_returns, start ="2022-01-04", end="2023-09-30")
+MSFT_returns_test <- window(MSFT_returns, start="2023-10-01")
+
 news_train <- window(news_ts, start ="2022-01-04", end="2023-09-30")
 news_test <- window(news_ts, start="2023-10-01")
+
 MSFT_VAR_Data <- cbind(MSFT_returns_train, news_train)
@@
 ```
+We see that almost none of the coefficients have a statistical significance as their p-values are all above 0.05.
+An exception is the second lag of MSFT returns.
+It seems to have a slight negative effect on the current price of MSFT.
+However, there is only small evidence.
 
-We see that almost none of the coefficients have a statistical significance.
-As a next step, we do a Granger causality test to confirm that news data is in fact non a causal driver for the MSFT stock price
+## Causlaity testing
+As a next step, we do a Granger causality test to confirm that our news sentiments are in fact not a causal driver for the MSFT stock price.
 
@@
 ```
-The p-value of 0.34 suggests that the gathered News sentiments are not a causal driver for the MSFT stock price. This leads us to reject our hypothesis.
+The p-value of 0.34 confirms that the gathered News sentiments are not a causal driver for the MSFT stock price. This leads us to reject our hypothesis.
 
-However, from a practical point of view, our VAR model may still be of some use when applied for forecasting purposes.
+## Forecasting
+From a practical point of view, our VAR model may still be of some use when applied for forecasting purposes.
 To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the news sentiment data of the testing period.
@@
 
-forecast <- predict(MSFT_VAR, newdata = forecast_data, n.ahead=43)
-plot(forecast)
-MSFT_VAR_pred <- forecast$fcst$MSFT_Returns
+MSFT_VAR_pred <- predict(MSFT_VAR, newdata = forecast_data, n.ahead=43)
+plot(MSFT_VAR_pred)
+MSFT_VAR_pred_values <- MSFT_VAR_pred$fcst$MSFT_Returns
 
-rmse_VAR <- sqrt(mean((MSFT_returns_test - MSFT_VAR_pred)^2))
-rmse_VAR
+rmse_VAR <- sqrt(mean((MSFT_returns_test - MSFT_VAR_pred_values)^2))
+cat("RMSE of VAR\t\t\t", rmse_VAR)
 
 MSFT_ARMA <- auto.arima(MSFT_returns_train)
+MSFT_ARMA
 MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(news_test))
@@
 rmse_ARMA <- sqrt(mean((MSFT_returns_test - MSFT_ARMA_pred$mean)^2))
-rmse_ARMA
+cat("RMSE of AR(2) Benchmark \t", rmse_ARMA)
 
 ```
-We see that auto.arima has found that the auto-regressive (AR) part of our benchmark ARMA model has an order of 2, since the coefficients ar1 and ar2 were estimated.
-The Absence of ma coefficients suggests that the Moving Average (MA) part has an order of 0.
-Therefore, we essentially deal with an AR(2) model as our benchmark.
+We see that auto.arima has found that the order of the auto-regressive (AR) as well as the Moving Average (MA) parts are of order 0.
+Therefore, we essentially deal with a mean model as our benchmark.
 During forecasting, we also see that it uses a mean of 0 with a confidence band for all future values.
@@
 
-While the VAR model reaches an RSME of 0.036 when compared to the truth values of our test set, the AR(2) benchmark reaches an RSME of 0.014.
-This means, our more sophisticated VAR model actually performs worse than the more simple AR(2) that is purely based on past values.
+While the VAR model reaches an RSME of 0.036 when compared to the truth values of our test set, the mean model benchmark reaches an RSME of 0.014.
+This means, our more sophisticated VAR model actually performs worse than the more simple benchmark that is purely based on the mean.
 
+# Conclusion
+To be added
 ```{r echo=FALSE, include=TRUE}
@@
 
-Bibliography:
+# Bibliography:
 

### 2023-12-17 MSFT.Rmd
sarima

@@
 library(ggplot2)
+library(utils)
+library(dplyr)
+library(xts)
+library(timeSeries)
 ```
+
 # Introduction 
@@
 First, we import the data and convert it to a time series so that we may plot it.
+After importing and converting our dataset into a workable format, we observed noticeable noise in the average_polarity data.
+To address this, we applied a LOESS smoothing technique.
+This method allows us to smooth out short-term fluctuations and highlight longer-term trends in sentiment data, crucial for correlating with stock price movements.
+The choice of the smoothing parameter (span) was iteratively refined to balance detail and smoothness
 
@@
 MSFT$average_polarity <- as.numeric(as.character(MSFT$average_polarity))
+# MSFT$Index <- as.Date(MSFT$Index)
 MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
 
-plot(MSFT_ts)
+# plot(MSFT_ts)
+
+events <- data.frame(
+  date = as.Date(c("2023-01-23", "2022-11-30", "2023-06-29", "2023-04-12", "2023-11-15")),
+  event = c(
+    "Microsoft investing 10 billion dollars into OpenAI",
+    "ChatGPT being released and created an AI-hype",
+    "Microsoft releasing Bing Co-Pilot and Microsoft Co-Pilot",
+    "The release of DALL-E 3 disrupting the image gen AI market",
+    "Sam Altman leaving OpenAI in November 2023"
+  )
+)
+
+# smooth polarity since it's very noisy
+ix.na = is.na(MSFT$average_polarity)
+problematic_values <- MSFT$average_polarity[ix.na]
+MSFT$average_polarity[problematic_values] <- NA
+# Replace with 0
+MSFT$average_polarity[problematic_values] <- 0
+MSFT$Index_numeric <- as.numeric(MSFT$Index - as.Date("2000-01-01"))
+MSFT$smoothed_polarity_loess <- with(MSFT, loess(average_polarity ~ Index_numeric, span = 0.2)$fitted)
+
+ggplot(data = MSFT, aes(x = Index)) +
+  geom_line(aes(y = MSFT.Adjusted, color = "MSFT.Adjusted"), size = 1) +
+  ylab("MSFT Adjusted Price") +
+
+  geom_line(aes(y = smoothed_polarity_loess * 2000, color = "Sentiment Average Score"), size = 1) +
+  ylab("Sentiment Average Score") +
+
+  scale_y_continuous(
+    name = "MSFT Adjusted Price",
+    sec.axis = sec_axis(~./2000, name = "Sentiment Average Score"),
+    limits = c(0, 400),
+    breaks = seq(0, 400, by = 50)
+  ) +
+
+  scale_color_manual(
+    values = c("MSFT.Adjusted" = "#00AFBB", "Sentiment Average Score" = "red"),
+    labels = c("MSFT Adjusted Price", "Sentiment Average Score")
+  ) +
+
+  ggtitle("MSFT Adjusted Price and Sentiment Average Score Over Time") +
+  theme_minimal()
 ```
@@
 cat("RMSE of VAR\t\t\t", rmse_VAR)
+```
 
+```{r echo=FALSE, include=TRUE}
 MSFT_ARMA <- auto.arima(MSFT_returns_train)
@@
 plot(MSFT_ARMA_pred)
+```
 
+```{r echo=FALSE, include=TRUE}
 rmse_ARMA <- sqrt(mean((MSFT_returns_test - MSFT_ARMA_pred$mean)^2))
@@
 This means, our more sophisticated VAR model actually performs worse than the more simple benchmark that is purely based on the mean.
+
+# Seasonal Adjustment
+
+### STL Decomposition
+
+After many trials of extracting seasonality by using the stl and decompose method and because the stock market data is not consistent because of holidays and the market is not open on a daily basis, here is another method to approach this problem using Fourier Transform:
+
+```{r echo=FALSE, include=TRUE}
+# Number of observations in the ime series
+n <- length(MSFT_returns)
+
+fourier <- data.frame(frequency = 1:(n/2), 
+                      spectrum = abs(fft(coredata(MSFT_returns)))[1:(n/2)])
+
+# Plot the Fourier Transform spectrum - can remove later
+ggplot(fourier, aes(x = frequency, y = spectrum)) +
+  geom_line() +
+  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
+  labs(title = "Fourier Transform of MSFT Adjusted Prices", 
+       x = "Frequency", 
+       y = "Amplitude")
+```
+
+We norice in this plot the presence of multiple peaks suggesting that there are several cyclical patterns in the data.
+This can happen if there are multiple underlying seasonalities or other forms of cyclical behavior.
+But there is not a single, dominant low-frequency component that clearly stands out.
+This suggests that the data might not have a strong trend or annual seasonality, or it may be masked by the noise.
+The problem is if we attempt to model all these frequencies, there's a risk of overfitting your time series model to the noise rather than to actual, meaningful seasonal patterns.
+
+### Reevaluating seasonality and trend
+```{r echo=FALSE, include=TRUE}
+# Convert to ts object, starting from the first date, with a frequency of 365 (daily data)
+start_date <- as.numeric(format(index(MSFT_returns)[1], "%Y")) + (as.numeric(format(index(MSFT_returns)[1], "%j")) - 1) / 365
+MSFT_returns_ts <- ts(MSFT_returns, start = start_date, frequency = 365)
+
+# Conduct a spectral analysis to identify significant frequencies
+spectrum_analysis <- spectrum(MSFT_returns_ts, spans = c(3, 5), plot = FALSE)
+
+# Identify peaks in the spectral density
+peak_frequencies <- which(diff(sign(diff(spectrum_analysis$spec))) == -2) + 1
+significant_frequencies <- spectrum_analysis$freq[peak_frequencies]
+significant_spectrum <- spectrum_analysis$spec[peak_frequencies]
+
+plot(spectrum_analysis$freq, spectrum_analysis$spec, type = 'l', xlab = 'Frequency', ylab = 'Spectral Density')
+points(significant_frequencies, significant_spectrum, col = 'red', pch = 19)
+```
+
+```{r echo=FALSE, include=TRUE}
+n <- length(MSFT_returns)
+# Extract seasonal components using Fourier series
+future_fourier_terms <- fourier(MSFT_returns_ts, K = length(significant_frequencies), h = 60) # 60 forecast horizon - 2 months
+
+# Model the seasonality by including Fourier terms as external regressors
+MSFT_seasonal_model <- auto.arima(MSFT_returns_ts, xreg = fourier_terms, seasonal = FALSE)
+summary(MSFT_seasonal_model)
+```
+The best-fit model for the series is an ARIMA(2,0,1).
+This model includes autoregressive (AR) terms, moving average (MA) terms, and various regression coefficients for exogenous variables.
+The model's log-likelihood is 1259.22, and it exhibits a reasonable AIC value, which suggest a good balance between model fit and complexity.
+The BIC value is also indicative of a well-fitting model.
+The training set error measures indicate that the model performs well on the training data, with a small mean error (ME) and low root mean squared error (RMSE) and mean absolute error (MAE).
+However, the MPE and MAPE are relatively high, suggesting some room for improvement in capturing certain patterns in the data.
+The MASE is 0.6607, and the autocorrelation of residuals (ACF1) is -0.0065.
+
+```{r echo=FALSE, include=TRUE}
+# Fit the time series model and make forecasts
+MSFT_forecast <- forecast(MSFT_seasonal_model, xreg = future_fourier_terms, h = 60)
+plot(MSFT_forecast)
+lines(MSFT_returns_test, col = 'red')
+```
+Calculate RMSE:
+```{r echo=FALSE, include=TRUE}
+actuals <- window(MSFT_returns_ts, start = c(2023, 118))
+rmse <- sqrt(mean((actuals - MSFT_forecast$mean)^2, na.rm = TRUE))
+cat("RMSE for Model with Fourier Terms: ", rmse)
+```
 

### 2023-12-17 MSFT_code_trials.R

@@ -1,6 +1,208 @@
 # This Script was used to get the Price data on MSFT, so that we can enrich
-# the data with News data and their sentiment scores via python script
+# the data with News data and their sentiment scores via python script included in this folder
 
+## Import Libraries
+library(utils)
+library(dplyr)
+library(ggplot2)
+library(scales)
+library(signal)
 library(quantmod)
-MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
-write.zoo(MSFT, "MSFT.csv", sep = ",", row.names = TRUE)
+
+# MSFT <- getSymbols.yahoo("MSFT", from="2022-01-01", to="2023-12-01", periodicity = "daily", auto.assign=FALSE)[,6]
+# write.zoo(MSFT, "MSFT.csv", sep = ",", row.names = TRUE)
+
+### Sentiment analysis
+data.vadar <- read.csv("data/final_data_vadar.csv")
+
+# Drop column the reddit pots since they are not needed for the analysis
+columns_to_drop <- c("worldnews", "stocks", "investing")
+data.vadar <- data.vadar[, -which(names(data.vadar) %in% columns_to_drop)]
+
+head(data.vadar)
+
+# Inspect the data
+str(data.vadar)
+
+# Convert the "Index" column to a Date type
+data.vadar$Index <- as.Date(data.vadar$Index)
+
+# Plot the average sentiment score against the MSFT.
+ggplot(data = data.vadar, aes(x = Index)) +
+  geom_line(aes(y = MSFT.Adjusted, color = "MSFT.Adjusted"), size = 1) +
+  ylab("MSFT Adjusted Price") +
+  
+  geom_line(aes(y = sentiment_average_score * 20, color = "Sentiment Average Score"), size = 1) +
+  ylab("Sentiment Average Score") +
+  
+  scale_y_continuous(
+    name = "MSFT Adjusted Price",
+    sec.axis = sec_axis(~./20, name = "Sentiment Average Score"),
+    limits = c(0, 400),
+    breaks = seq(0, 400, by = 50)
+  ) +
+  
+  scale_color_manual(
+    values = c("MSFT.Adjusted" = "#00AFBB", "Sentiment Average Score" = "red"),
[…]

### 2023-12-18 MSFT.Rmd
SARIMA

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
+
 ```
@@
 
-```{r echo=FALSE, include=TRUE}
+```{r plot_chunk, fig.height=10, fig.width=14, echo=FALSE, include=TRUE}
 MSFT <- read.csv("data/final_data.csv")
@@
 MSFT$average_polarity <- as.numeric(as.character(MSFT$average_polarity))
-# MSFT$Index <- as.Date(MSFT$Index)
 MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
-
-# plot(MSFT_ts)
 
@@
   event = c(
-    "Microsoft investing 10 billion dollars into OpenAI",
-    "ChatGPT being released and created an AI-hype",
-    "Microsoft releasing Bing Co-Pilot and Microsoft Co-Pilot",
-    "The release of DALL-E 3 disrupting the image gen AI market",
-    "Sam Altman leaving OpenAI in November 2023"
+    "Investing into OpenAI",
+    "ChatGPT",
+    "Bing Co-Pilot Release",
+    "DALL-E 3 Release",
+    "Sam Altman Drama"
   )
@@
 
-# smooth polarity since it's very noisy
+event_data <- merge(events, MSFT, by.x = "date", by.y = "Index", all.x = TRUE)
+
 ix.na = is.na(MSFT$average_polarity)
@@
 
-ggplot(data = MSFT, aes(x = Index)) +
+main_plot <- ggplot(data = MSFT, aes(x = Index)) +
   geom_line(aes(y = MSFT.Adjusted, color = "MSFT.Adjusted"), size = 1) +
@@
   theme_minimal()
+
+# Adjust the legend size and position
+main_plot <- main_plot + theme(legend.position = c(0.15, 0.2), 
+                               legend.background = element_blank(), # Transparent background
+                               legend.key = element_blank(), 
+                               legend.text = element_text(size = 8)) # Smaller text size
+
+# arrows and text layer
+arrows_layer <- ggplot(event_data, aes(x = date, y = MSFT.Adjusted, label = event)) +
+  geom_segment(aes(xend = date, yend = MSFT.Adjusted - 20), 
+               arrow = arrow(type = "closed", length = unit(0.1, "inches")),
+               size = 0.5) +
+  labs(x = NULL, y = NULL) +  # Remove axis labels
+  geom_text(hjust = 0.6, vjust = -0.7, size = 2.5, color = "black") +  # Add text
+  labs(x = NULL, y = NULL) +  
+  theme_void()
+
+combined_plot <- main_plot + annotation_custom(
+  ggplotGrob(arrows_layer),
+  xmin = min(event_data$date), xmax = max(event_data$date),
+  ymin = min(event_data$MSFT.Adjusted) + 10, ymax = max(event_data$MSFT.Adjusted) + 10
+)
+
+print(combined_plot)
 ```
@@
 cat("RMSE of AR(2) Benchmark \t", rmse_ARMA)
-
 ```
@@
 
-### STL Decomposition
-
-After many trials of extracting seasonality by using the stl and decompose method and because the stock market data is not consistent because of holidays and the market is not open on a daily basis, here is another method to approach this problem using Fourier Transform:
+After many trials of extracting seasonality by using the STL and decompose method, we approached the problem using Fourier Transform due to the inconsistent nature of stock market data.
 
@@
 
-We norice in this plot the presence of multiple peaks suggesting that there are several cyclical patterns in the data.
+We notice in this plot the presence of multiple peaks suggesting that there are several cyclical patterns in the data.
 This can happen if there are multiple underlying seasonalities or other forms of cyclical behavior.
@@
 The problem is if we attempt to model all these frequencies, there's a risk of overfitting your time series model to the noise rather than to actual, meaningful seasonal patterns.
+
+Our Fourier analysis revealed multiple periodicities within the time series, suggesting complex seasonality.
+While including multiple Fourier terms can model these patterns, there is a risk of overfitting, especially if the data may contain noise masquerading as seasonal effects.
+To avoid this, we considered models that use a reduced set of Fourier terms, focusing only on the most significant frequencies.
+We also explored alternative methods, such as wavelet analysis, which can handle multiple levels of seasonality without assuming a fixed cycle length.
+These techniques allow us to capture the most important seasonal effects while reducing the risk of overfitting to the noise in the data.
 
@@
 ```
+## Model Selection
+
+Based on the results of the Fourier analysis, we found it prudent to look for a model that would allow greater flexibility in capturing the identified seasonal patterns without overfitting.
+This led us to consider the ARIMA model, which can be augmented with Fourier terms to account for the complex seasonality observed.
+The ARIMA model was chosen for its ability to model non-seasonal and seasonal lags of the differenced series, which makes it suitable for our data, which exhibit non-stationarity.
+In addition, the inclusion of Fourier terms allows us to incorporate the significant seasonal frequencies identified earlier, providing a robust approach to capturing the underlying patterns in the data.
 
@@
 # Extract seasonal components using Fourier series
-future_fourier_terms <- fourier(MSFT_returns_ts, K = length(significant_frequencies), h = 60) # 60 forecast horizon - 2 months
+future_fourier_terms <- fourier(MSFT_returns_ts, K = length(significant_frequencies), h = n) # 60 forecast horizon - 2 months
 
 # Model the seasonality by including Fourier terms as external regressors
-MSFT_seasonal_model <- auto.arima(MSFT_returns_ts, xreg = fourier_terms, seasonal = FALSE)
+MSFT_seasonal_model <- auto.arima(MSFT_returns_ts, xreg = future_fourier_terms, seasonal = FALSE)
 summary(MSFT_seasonal_model)
@@
 
+## Forecasting with the ARIMA Model
+
+With our chosen model, we proceeded to forecasting. Here, we assess the model's predictive capability and compare its performance against a simpler benchmark model.
+
 ```{r echo=FALSE, include=TRUE}
 # Fit the time series model and make forecasts
-MSFT_forecast <- forecast(MSFT_seasonal_model, xreg = future_fourier_terms, h = 60)
+MSFT_forecast <- forecast(MSFT_seasonal_model, xreg = future_fourier_terms, h = length(MSFT_returns_test))
 plot(MSFT_forecast)
@@
 ```{r echo=FALSE, include=TRUE}
-actuals <- window(MSFT_returns_ts, start = c(2023, 118))
+actuals <- coredata(MSFT_returns_test)
 rmse <- sqrt(mean((actuals - MSFT_forecast$mean)^2, na.rm = TRUE))
-cat("RMSE for Model with Fourier Terms: ", rmse)
+cat("RMSE for Model with Fourier Terms: ", rmse, "\n")
 ```
+## Forecasting Discussion:
+
+In the forecasting section, you compare the performance of the ARIMA model with a benchmark model.
+It would be beneficial to discuss the implications of these results in more detail, explaining why the benchmark might perform better and what this suggests about the predictability of the stock price.
 
 # Conclusion
-To be added
-```{r echo=FALSE, include=TRUE}
 
-```
+In summary, our comprehensive analysis using an ARIMA model with Fourier terms suggests that while there is a discernible pattern in the data, it is not strongly influenced by news sentiment as originally hypothesized.
+The non-significant results of the Granger causality test, coupled with the model's performance metrics, indicate that Microsoft's stock price movements are likely driven by factors not captured by news sentiment from the selected subreddits.
+The model's predictive performance indicates an area for potential improvement over a simpler benchmark model.
+
+# Future work
+
+For future research, we recommend investigating additional variables that may better explain the variance in Microsoft stock prices, such as economic indicators, market indices, or sentiment from a broader range of news sources.
+It may also be beneficial to incorporate machine learning models capable of capturing non-linear relationships within the data.
+In addition, expanding the dataset to include high-frequency trading data could provide more granular insights into the impact of news events.
+Continued refinement of the model, including exploration of non-traditional forms of seasonality, will be critical to improving the predictive power of our analysis.
 

### 2023-12-18 MSFT_code_trials.R

@@ -142,11 +142,11 @@ MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
 events <- data.frame(
   date = as.Date(c("2023-01-23", "2022-11-30", "2023-06-29", "2023-04-12", "2023-11-15")),
   event = c(
-    "Microsoft investing 10 billion dollars into OpenAI",
-    "ChatGPT being released and created an AI-hype",
-    "Microsoft releasing Bing Co-Pilot and Microsoft Co-Pilot",
-    "The release of DALL-E 3 disrupting the image gen AI market",
-    "Sam Altman leaving OpenAI in November 2023"
+    "Investing into OpenAI",
+    "ChatGPT",
+    "Bing Co-Pilot Release",
+    "DALL-E 3 Release",
+    "Sam Altman Drama"
   )
 )
 
@@ -189,11 +189,13 @@ existing_plot <- ggplot(data = MSFT, aes(x = Index)) +
   theme_minimal()
 
 # Create the arrows layer
-arrows_layer <- ggplot(event_data, aes(x = date, y = MSFT.Adjusted)) +
+arrows_layer <- ggplot(event_data, aes(x = date, y = MSFT.Adjusted, label = event)) +
   geom_segment(aes(xend = date, yend = MSFT.Adjusted - 20), 
                arrow = arrow(type = "closed", length = unit(0.2, "inches")),
                size = 0.5) +
   labs(x = NULL, y = NULL) +  # Remove axis labels
+  geom_text(hjust = 0.6, vjust = -0.3, size = 2.5, color = "black") +  # Add text
+  labs(x = NULL, y = NULL) +  
   theme_void()
 
 # Combine the existing plot and the arrows layer

### 2023-12-18 MSFT_with_vadar_analysis/MSFT_vadar_analysis.Rmd
VAR with vadar sentiment analysis

--- 2023-12-18 MSFT.Rmd
@@
 First, we import the data and convert it to a time series so that we may plot it.
-After importing and converting our dataset into a workable format, we observed noticeable noise in the average_polarity data.
+After importing and converting our dataset into a workable format, we observed noticeable noise in the sentiment_average_score data.
 To address this, we applied a LOESS smoothing technique.
@@
 ```{r plot_chunk, fig.height=10, fig.width=14, echo=FALSE, include=TRUE}
-MSFT <- read.csv("data/final_data.csv")
+MSFT <- read.csv("final_data_vadar.csv")
 MSFT$Index <- as.Date(MSFT$Index)
 MSFT$MSFT.Adjusted <- as.numeric(as.character(MSFT$MSFT.Adjusted))
-MSFT$average_polarity <- as.numeric(as.character(MSFT$average_polarity))
+MSFT$sentiment_average_score <- as.numeric(as.character(MSFT$sentiment_average_score))
 MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
@@
 
-ix.na = is.na(MSFT$average_polarity)
-problematic_values <- MSFT$average_polarity[ix.na]
-MSFT$average_polarity[problematic_values] <- NA
+ix.na = is.na(MSFT$sentiment_average_score)
+problematic_values <- MSFT$sentiment_average_score[ix.na]
+MSFT$sentiment_average_score[problematic_values] <- NA
 # Replace with 0
-MSFT$average_polarity[problematic_values] <- 0
+MSFT$sentiment_average_score[problematic_values] <- 0
 MSFT$Index_numeric <- as.numeric(MSFT$Index - as.Date("2000-01-01"))
-MSFT$smoothed_polarity_loess <- with(MSFT, loess(average_polarity ~ Index_numeric, span = 0.2)$fitted)
+MSFT$smoothed_polarity_loess <- with(MSFT, loess(sentiment_average_score ~ Index_numeric, span = 0.2)$fitted)
 
@@
 
-  geom_line(aes(y = smoothed_polarity_loess * 2000, color = "Sentiment Average Score"), size = 1) +
+  geom_line(aes(y = sentiment_average_score, color = "Sentiment Average Score"), size = 1) +
   ylab("Sentiment Average Score") +
@@
 ```{r echo=FALSE, include=TRUE}
-news_ts <- zoo(MSFT$average_polarity, order.by = MSFT$Index)
+news_ts <- zoo(MSFT$sentiment_average_score, order.by = MSFT$Index)
 
@@
 ```
-We see that almost none of the coefficients have a statistical significance as their p-values are all above 0.05.
-An exception is the second lag of MSFT returns.
-It seems to have a slight negative effect on the current price of MSFT.
-However, there is only small evidence.
+The coefficient test reveals some interesting insights into the dynamics between MSFT stock returns and news sentiment.
+In particular, several lagged values of news sentiment exhibit statistical significance, suggesting a nuanced, albeit modest, effect on stock returns.
+For example, both the second and fifth lags of sentiment show a negative impact, while the eighth lag shows a more pronounced negative impact.
+This pattern is mirrored by the eleventh and fifteenth lags, but with less statistical strength.
+Conversely, the impact of news sentiment is not uniform across all lags, as some show a positive relationship, although these are not statistically significant at conventional levels.
+
+These findings suggest that while news sentiment does not consistently drive stock returns, it does have some predictive power at certain intervals.
+This time effect could be due to the market's lagged reaction to news sentiment or to the complex interplay between various market forces and investor psychology.
 
@@
 ```
-The p-value of 0.34 confirms that the gathered News sentiments are not a causal driver for the MSFT stock price. This leads us to reject our hypothesis.
+he Granger causality test provided a new perspective on the relationship between news sentiment and MSFT stock returns.
+Contrary to our initial hypothesis, the test indicates that news sentiment may indeed have a Granger causal effect on stock returns, as indicated by a p-value of 0.008237.
+This result is statistically significant at conventional levels (p < 0.05), leading us to reconsider our previous stance.
+With an F-test value of 2.1049 and degrees of freedom of 15 and 782 for the numerator and denominator, respectively, we find evidence that past values of news sentiment contain information that is useful in predicting future values of MSFT stock returns.
+
+This finding calls for a reevaluation of the dynamic interplay between public sentiment, as captured by news, and subsequent investor behavior, as reflected in stock prices.
+It suggests that the informational content of news sentiment is indeed incorporated into market prices, albeit with a degree of complexity that may require further research to fully understand.
+
+In light of this finding, our initial belief in the non-causal role of news sentiment may have been premature.
+This reinforces the need for a multifaceted approach to the analysis of financial time series, where causality may not always be apparent at first glance, but may emerge upon closer examination.
 

### 2023-12-21 MSFT.Rmd
hopefully final report

@@
 library(vars)
+library(urca)
 library(tseries)
@@
 
+# lag.max = 24 is a starting point for high-frequency data (like daily data), 
+# we consider a larger maximum lag because there could be significant autocorrelations over several days.
 MSFT_VAR <- VAR(MSFT_VAR_Data, ic="AIC", lag.max = 24)
@@
 However, there is only small evidence.
+
+We tried another method of sentiment analysis, VADER (Valence Aware Dictionary and Sentiment Reasoner) is a lexicon and rule-based sentiment analysis tool that assigns sentiment scores to words and combines them to determine the overall sentiment polarity and intensity of a piece of text, with a focus on handling sentiment expressions in informal language such as social media:
+
+```{r echo=FALSE, include=TRUE}
+MSFT.vadar <- read.csv("data/final_data_vadar.csv")
+MSFT.vadar$Index <- as.Date(MSFT.vadar$Index)
+MSFT.vadar$MSFT.Adjusted <- as.numeric(as.character(MSFT.vadar$MSFT.Adjusted))
+MSFT.vadar$sentiment_average_score <- as.numeric(as.character(MSFT.vadar$sentiment_average_score))
+MSFT.vadar_ts <- zoo(MSFT.vadar$MSFT.Adjusted, order.by = MSFT.vadar$Index)
+MSFT.vadar_returns <- na.omit(diff(log(MSFT.vadar_ts)))
+
+vadar.news_ts <- zoo(MSFT.vadar$sentiment_average_score, order.by = MSFT.vadar$Index)
+
+MSFT.vadar_returns_train <- window(MSFT.vadar_returns, start ="2022-01-04", end="2023-09-30")
+MSFT.vadar_returns_test <- window(MSFT.vadar_returns, start="2023-10-01")
+
+vadar.news_train <- window(vadar.news_ts, start ="2022-01-04", end="2023-09-30")
+vadar.news_test <- window(vadar.news_ts, start="2023-10-01")
+
+MSFT.vadar_VAR_Data <- cbind(MSFT.vadar_returns_train, vadar.news_train)
+colnames(MSFT.vadar_VAR_Data) <- c("MSFT_Returns", "News_Sentiment")
+
+MSFT.vadar_VAR <- VAR(MSFT.vadar_VAR_Data, ic="AIC", lag.max = 24)
+coeftest(MSFT.vadar_VAR)
+```
+Overall, this VAR model on the new sentiment analysis indicates that certain past values Microsoft stock returns and reddit posts have a significant impact on the current values of these variables.
+The model suggests a complex interplay between stock returns and reddit posts sentiment with specific lags being more influential than others.
+However, many of the coefficients are not significant, suggesting that not all past values are equally informative for predicting current values.
 
@@
 
+```{r echo=FALSE, include=TRUE}
+# Casuality test for VADAR
+causality(MSFT.vadar_VAR, cause="News_Sentiment")["Granger"] 
+```
+The p-value of 0.008237 from the Granger causality test suggests that reddit posts sentiment is indeed a causal driver of MSFT stock price.
+This result leads us to accept the hypothesis that changes in news sentiment have a predictive effect on Microsoft stock returns.
+
 ## Forecasting
-From a practical point of view, our VAR model may still be of some use when applied for forecasting purposes.
-To see if the inclusion of the news sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the news sentiment data of the testing period.
+We will use the VADAR VAR model for forecasting purposes to see if the inclusion of the reddit posts sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the reddit posts sentiment data of the testing period.
 
@@
 forecast_data <- data.frame(
-  MSFT_Returns = rep(NA, length(news_test)),
-  News_Sentiment = news_test
+  MSFT_Returns = rep(NA, length(vadar.news_test)),
+  News_Sentiment = vadar.news_test
 )
 
-MSFT_VAR_pred <- predict(MSFT_VAR, newdata = forecast_data, n.ahead=43)
+MSFT_VAR_pred <- predict(MSFT.vadar_VAR, newdata = forecast_data, n.ahead=43)
 plot(MSFT_VAR_pred)
@@
 
-rmse_VAR <- sqrt(mean((MSFT_returns_test - MSFT_VAR_pred_values)^2))
+rmse_VAR <- sqrt(mean((MSFT.vadar_returns_test - MSFT_VAR_pred_values)^2))
 cat("RMSE of VAR\t\t\t", rmse_VAR)
@@
 ```{r echo=FALSE, include=TRUE}
-MSFT_ARMA <- auto.arima(MSFT_returns_train)
+MSFT_ARMA <- auto.arima(MSFT.vadar_returns_train)
 MSFT_ARMA
-MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(news_test))
+MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(vadar.news_test))
 plot(MSFT_ARMA_pred)
@@
 ```{r echo=FALSE, include=TRUE}
-rmse_ARMA <- sqrt(mean((MSFT_returns_test - MSFT_ARMA_pred$mean)^2))
+rmse_ARMA <- sqrt(mean((MSFT.vadar_returns_test - MSFT_ARMA_pred$mean)^2))
 cat("RMSE of AR(2) Benchmark \t", rmse_ARMA)
@@
 
-In summary, our comprehensive analysis using an ARIMA model with Fourier terms suggests that while there is a discernible pattern in the data, it is not strongly influenced by news sentiment as originally hypothesized.
-The non-significant results of the Granger causality test, coupled with the model's performance metrics, indicate that Microsoft's stock price movements are likely driven by factors not captured by news sentiment from the selected subreddits.
+In summary, our comprehensive analysis using an ARIMA model with the addition of VADER sentiment analysis suggests offers new insights into the influence of reddit posts sentiment on Microsoft's stock price.
+The updated Granger causality test results from the VADER model indicate a possible predictive effect of subreddit sentiment on stock returns, a finding that warrants further exploration.
+While the earlier model did not show a strong sentiment impact, the VADER analysis suggests that sentiment may play a role, although it may not be the primary driver of stock movements.
+The significant results of the Granger causality test, coupled with the model's performance metrics, indicate that Microsoft's stock price movements are likely driven by factors not captured by news sentiment from the selected subreddits.
 The model's predictive performance indicates an area for potential improvement over a simpler benchmark model.
+In addition, our examination of seasonality using the Fourier transform revealed complex seasonal patterns in the data.
+This suggests that stock price movements may be influenced by a combination of factors, including subtle seasonal trends and shifts in sentiment.
+Our findings suggest potential areas for improvement in modeling and forecasting, and underscore the need for models that can capture these multifaceted influences.
 
@@
 Roni Bhowmik, Gouranga Chandra Debnath, Nitai Chandra Debnath, Shouyang Wang (2022); Emerging stock market reactions to shocks during various crisis periods 2022). DOI 10.1371/journal.pone.0272450
+
+"The Causal Relationship between Social Media Sentiment and Stock Return: Experimental Evidence from an Online Message Forum" by Lin et al.
+(2022) examines the causal effect of social media sentiment on stock returns using an experimental approach.
+The study finds that positive sentiment can significantly increase same-day stock prices, but the effect is short-lived.
+
+"Impact Of Social Media On Stock Market- A Case Of Sentiment Analysis Using Vader" by Kumar et al.
+(2021) applies the Vader sentiment analysis tool to Twitter data to assess its impact on stock market movements.
+The study finds that positive sentiment tweets are associated with increased stock prices, while negative sentiment tweets are associated with decreased stock prices.

### 2023-12-21 MSFT_with_vadar_analysis/MSFT_vadar_analysis.Rmd
hopefully final report

@@
 MSFT <- read.csv("final_data_vadar.csv")
-MSFT$Index <- as.Date(MSFT$Index)
+# MSFT$Index <- as.Date(MSFT$Index)
 MSFT$MSFT.Adjusted <- as.numeric(as.character(MSFT$MSFT.Adjusted))
-MSFT$sentiment_average_score <- as.numeric(as.character(MSFT$sentiment_average_score))
 MSFT_ts <- zoo(MSFT$MSFT.Adjusted, order.by = MSFT$Index)
 
-events <- data.frame(
-  date = as.Date(c("2023-01-23", "2022-11-30", "2023-06-29", "2023-04-12", "2023-11-15")),
-  event = c(
-    "Investing into OpenAI",
-    "ChatGPT",
-    "Bing Co-Pilot Release",
-    "DALL-E 3 Release",
-    "Sam Altman Drama"
-  )
-)
+MSFT$Index <- as.Date(MSFT$Index)
+ratio <- max(MSFT$MSFT.Adjusted, na.rm = TRUE) / max(MSFT$sentiment_average_score, na.rm = TRUE)
 
-event_data <- merge(events, MSFT, by.x = "date", by.y = "Index", all.x = TRUE)
+# Create a basic plot
+p <- ggplot(MSFT, aes(x = Index)) +
+  geom_line(aes(y = MSFT.Adjusted, colour = "MSFT Adjusted")) +
+  geom_line(aes(y = sentiment_average_score, colour = "Sentiment Average Score")) +
+  scale_colour_manual("", 
+                      breaks = c("MSFT Adjusted", "Sentiment Average Score"),
+                      values = c("blue", "red")) +
+  scale_y_continuous(
+    "MSFT Adjusted",
+    sec.axis = sec_axis(~ . / ratio, name = "Sentiment Average Score")
+  ) +
+  labs(title = "MSFT Adjusted and Sentiment Average Score Over Time",
+       x = "Date",
+       y = "MSFT Adjusted")
 
-ix.na = is.na(MSFT$sentiment_average_score)
-problematic_values <- MSFT$sentiment_average_score[ix.na]
-MSFT$sentiment_average_score[problematic_values] <- NA
-# Replace with 0
-MSFT$sentiment_average_score[problematic_values] <- 0
-MSFT$Index_numeric <- as.numeric(MSFT$Index - as.Date("2000-01-01"))
-MSFT$smoothed_polarity_loess <- with(MSFT, loess(sentiment_average_score ~ Index_numeric, span = 0.2)$fitted)
-
-main_plot <- ggplot(data = MSFT, aes(x = Index)) +
-  geom_line(aes(y = MSFT.Adjusted, color = "MSFT.Adjusted"), size = 1) +
-  ylab("MSFT Adjusted Price") +
-
-  geom_line(aes(y = sentiment_average_score, color = "Sentiment Average Score"), size = 1) +
-  ylab("Sentiment Average Score") +
-
-  scale_y_continuous(
-    name = "MSFT Adjusted Price",
-    sec.axis = sec_axis(~./2000, name = "Sentiment Average Score"),
-    limits = c(0, 400),
-    breaks = seq(0, 400, by = 50)
-  ) +
-
-  scale_color_manual(
-    values = c("MSFT.Adjusted" = "#00AFBB", "Sentiment Average Score" = "red"),
-    labels = c("MSFT Adjusted Price", "Sentiment Average Score")
-  ) +
-
-  ggtitle("MSFT Adjusted Price and Sentiment Average Score Over Time") +
-  theme_minimal()
-
-# Adjust the legend size and position
-main_plot <- main_plot + theme(legend.position = c(0.15, 0.2), 
-                               legend.background = element_blank(), # Transparent background
-                               legend.key = element_blank(), 
-                               legend.text = element_text(size = 8)) # Smaller text size
-
-# arrows and text layer
-arrows_layer <- ggplot(event_data, aes(x = date, y = MSFT.Adjusted, label = event)) +
-  geom_segment(aes(xend = date, yend = MSFT.Adjusted - 20), 
-               arrow = arrow(type = "closed", length = unit(0.1, "inches")),
-               size = 0.5) +
-  labs(x = NULL, y = NULL) +  # Remove axis labels
-  geom_text(hjust = 0.6, vjust = -0.7, size = 2.5, color = "black") +  # Add text
-  labs(x = NULL, y = NULL) +  
-  theme_void()
-
-combined_plot <- main_plot + annotation_custom(
-  ggplotGrob(arrows_layer),
-  xmin = min(event_data$date), xmax = max(event_data$date),
-  ymin = min(event_data$MSFT.Adjusted) + 10, ymax = max(event_data$MSFT.Adjusted) + 10
-)
-
-print(combined_plot)
+# Show the plot
+print(p)
 ```

### 2023-12-22 MSFT.Rmd
final fixes

@@
 Hereby MSFT price data was downloaded through the Yahoo API in R and Reddit posts were scraped using Jupyter Notebooks.
-The python libraries nltk, textblob and wordlcoud were of support in the creation of the sentiment scores.
+The python libraries nltk, textblob, VADER (Kumar et al.
+2021) and wordlcoud were of support in the creation of the sentiment scores.
+VADER (Valence Aware Dictionary and Sentiment Reasoner) is a lexicon and rule-based sentiment analysis tool that assigns sentiment scores to words and combines them to determine the overall sentiment polarity and intensity of a piece of text, with a focus on handling sentiment expressions in informal language such as social media.
 
@@
 MSFT_returns <- na.omit(diff(log(MSFT_ts)))
+plot(MSFT_returns)
+```
 
-plot(MSFT_returns)
+```{r echo=FALSE, include=TRUE}
 adf.test(MSFT_returns)
@@
 We divide the dataset into a Train/Test Split, whereas November and December 2023 will serve as a test set for later predicitions.
-
 First we create a time series of news sentiment data.
@@
 This will be our basis to check whether News are a causal driver for MSFT price returns.
-
 We then do a coefficient test, to get more information on the statistical significance of the coefficients of our VAR Model.
@@
 
-We tried another method of sentiment analysis, VADER (Valence Aware Dictionary and Sentiment Reasoner) is a lexicon and rule-based sentiment analysis tool that assigns sentiment scores to words and combines them to determine the overall sentiment polarity and intensity of a piece of text, with a focus on handling sentiment expressions in informal language such as social media:
+We tried another method of sentiment analysis, VADER:
 
@@
 plot(MSFT_VAR_pred)
+```
+
+```{r echo=FALSE, include=TRUE}
 MSFT_VAR_pred_values <- MSFT_VAR_pred$fcst$MSFT_Returns
-
 rmse_VAR <- sqrt(mean((MSFT.vadar_returns_test - MSFT_VAR_pred_values)^2))
@@
 MSFT_ARMA
+```
+
+```{r echo=FALSE, include=TRUE}
 MSFT_ARMA_pred <- forecast(MSFT_ARMA, level=95, h = length(vadar.news_test))
@@
 This suggests that the data might not have a strong trend or annual seasonality, or it may be masked by the noise.
-The problem is if we attempt to model all these frequencies, there's a risk of overfitting your time series model to the noise rather than to actual, meaningful seasonal patterns.
+The problem is if we attempt to model all these frequencies, there's a risk of overfitting the time series model to the noise rather than to actual, meaningful seasonal patterns.
 
-Our Fourier analysis revealed multiple periodicities within the time series, suggesting complex seasonality.
-While including multiple Fourier terms can model these patterns, there is a risk of overfitting, especially if the data may contain noise masquerading as seasonal effects.
-To avoid this, we considered models that use a reduced set of Fourier terms, focusing only on the most significant frequencies.
 We also explored alternative methods, such as wavelet analysis, which can handle multiple levels of seasonality without assuming a fixed cycle length.
@@
 
-### Reevaluating seasonality and trend
 ```{r echo=FALSE, include=TRUE}
@@
 ```
-## Model Selection
+
+### Model Selection
 
@@
 ```
-## Forecasting Discussion:
-
-In the forecasting section, you compare the performance of the ARIMA model with a benchmark model.
-It would be beneficial to discuss the implications of these results in more detail, explaining why the benchmark might perform better and what this suggests about the predictability of the stock price.
 
@@
 
-Agus Shuarsono, Auliya Aziza and Wara Pramesti (2017); Comparison of vector autoregressive (VAR) and vector error correction models (VECM) for index of ASEAN stock price. DOI 10.1063/1.5016666
+- Agus Shuarsono, Auliya Aziza and Wara Pramesti (2017); Comparison of vector autoregressive (VAR) and vector error correction models (VECM) for index of ASEAN stock price. DOI 10.1063/1.5016666
 
-Aptech, Introduction to the Fundamentals of Vector Autoregressive Models (2021). https://www.aptech.com/blog/introduction-to-the-fundamentals-of-vector-autoregressive-models/
+- Aptech, Introduction to the Fundamentals of Vector Autoregressive Models (2021). https://www.aptech.com/blog/introduction-to-the-fundamentals-of-vector-autoregressive-models/
 
-Microsoft, 2022 a look back at a year of accelerating progress in AI.
+- Microsoft, 2022 a look back at a year of accelerating progress in AI.
 https://www.microsoft.com/en-us/research/blog/2022-a-look-back-at-a-year-of-accelerating-progress-in-ai/
 
-Roni Bhowmik, Gouranga Chandra Debnath, Nitai Chandra Debnath, Shouyang Wang (2022); Emerging stock market reactions to shocks during various crisis periods 2022). DOI 10.1371/journal.pone.0272450
+- Roni Bhowmik, Gouranga Chandra Debnath, Nitai Chandra Debnath, Shouyang Wang (2022); Emerging stock market reactions to shocks during various crisis periods 2022). DOI 10.1371/journal.pone.0272450
 
-"The Causal Relationship between Social Media Sentiment and Stock Return: Experimental Evidence from an Online Message Forum" by Lin et al.
-(2022) examines the causal effect of social media sentiment on stock returns using an experimental approach.
-The study finds that positive sentiment can significantly increase same-day stock prices, but the effect is short-lived.
+- Wang, X., Xiang, Z., Xu, W., & Yuan, P.
+(2022).
+The causal relationship between social media sentiment and stock return: Experimental evidence from an online message forum.
+Economics Letters, 216.
+[Link](https://doi.org/10.1016/j.econlet.2022.110598&#8203)
 
-"Impact Of Social Media On Stock Market- A Case Of Sentiment Analysis Using Vader" by Kumar et al.
-(2021) applies the Vader sentiment analysis tool to Twitter data to assess its impact on stock market movements.
-The study finds that positive sentiment tweets are associated with increased stock prices, while negative sentiment tweets are associated with decreased stock prices.
+- Singh, A., Singh, J., & Ghosal, A.
+(2022).
+Impact of social media on stock market- A case of sentiment analysis using Vader.
+In 2022 International Conference on Machine Learning Big Data Cloud and Parallel Computing (COM-IT-CON).
+[link](https://doi.org/10.1109/COM-IT-CON54601.2022.9850668&#8203)

### 2024-01-21 Zedan_Wullschleger_MSFT_project/MSFT.Rmd
final commit

--- 2023-12-22 MSFT.Rmd
@@
 ```{r echo=FALSE, include=TRUE}
-# Casuality test for VADAR
+# Casuality test for VADER
 causality(MSFT.vadar_VAR, cause="News_Sentiment")["Granger"] 
@@
 ## Forecasting
-We will use the VADAR VAR model for forecasting purposes to see if the inclusion of the reddit posts sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the reddit posts sentiment data of the testing period.
+We will use the VADER VAR model for forecasting purposes to see if the inclusion of the reddit posts sentiment in our model has an improving effect on the models accuracy when predicting the price movements of MSFT we do some forecasting for our testing period where we include the reddit posts sentiment data of the testing period.
 
